---
title: "R Notebook"
author: "Ishaan Yadav"
output:
  word_document: default
  html_notebook: default
---



```{r}
df<-read.csv("C:/Users/Admin/Downloads/Expt 2- Data set_Travelled abroad_csv.csv")
head(df)
```
1.	Find out the % of Indians in the sample who have travelled abroad using the data source.
```{r}
percen=nrow(subset(df,Travelledabroad=='Y'))/nrow(df)*100
cat("Percentage of Indians in the sample who have tarvelled aboard is :",percen,"%")
```
2.	Treating this value as ‘p’, calculate the following probabilities –
a.	What is the probability that in a randomly chosen sample of 10 persons, no one has travelled abroad?

```{r}
ans4=dbinom(0,10,0.56)
ans4
```
b.	What is the probability that in a randomly chosen sample of 10 persons, exactly one has travelled abroad?
```{r}
ans5=dbinom(1,10,0.56)
ans5
```
c.	What is the probability that in a randomly chosen sample of 10 persons, exactly two persons have travelled abroad?
```{r}
ans6=dbinom(2,10,0.56)
ans6
```
d.	What is the probability that in a randomly chosen sample of 10 persons, exactly three persons have travelled abroad?
```{r}
```


```{r}
ansd=dbinom(3,10,0.56)
ansd
```

e.	What is the probability that in a randomly chosen sample of 10 persons, exactly four persons have travelled abroad?

```{r}
anse=dbinom(4,10,0.56)
anse
```
f.	What is the probability that in a randomly chosen sample of 10 persons, exactly five persons have travelled abroad.
```{r}
ansf=dbinom(5,10,0.56)
ansf
```
g.	What is the probability that in a randomly chosen sample of 10 persons, exactly six persons have travelled abroad?
```{r}
ansg=dbinom(6,10,0.56)
ansg
```
h.	What is the probability that in a randomly chosen sample of 10 persons, exactly seven persons have travelled abroad?
```{r}
ansh=dbinom(7,10,0.56)
ansh
```
i.	What is the probability that in a randomly chosen sample of 10 persons, exactly eight persons have travelled abroad?
```{r}
ansi=dbinom(8,10,0.56)
ansi
```
j.	What is the probability that in a randomly chosen sample of 10 persons, exactly nine persons have travelled abroad?
```{r}
ansj=dbinom(9,10,0.56)
ansj
```
k.	What is the probability that in a randomly chosen sample of 10 persons, all 10 persons have travelled abroad? 
```{r}
ansk=dbinom(10,10,0.56)
ansk
```
3.	Plot the probability values as a Table / Bar graph/plot and interpret plot.
```{r}
barplot(dbinom(0:10,10,0.56))
```
Interpretation:Binomial probablities in this example are nearly normally distributed

4.	What is the probability that in the randomly chosen sample of 100 persons at least 59 have travelled abroad?  
Hint: Expected to perform Normal approximation for the binary distribution. 
```{r}
ansp=pbinom(59,100,0.56,lower.tail=F)
ansd=dbinom(59,100,0.56)  #including the i th value that is 59
ansp+ansd
```
Using normal approxiamation to binomail distribution
```{r}

mu<-100*0.56
sigma<-sqrt(100*0.56*(1-0.56))
pnorm(58.5,mu,sigma,lower.tail=F)

```
