---
title: "performane Matrices"
author: "Ishaan Yadav"
output:
  word_document: default
  html_notebook: default
---
Import data
```{r}
df<-read.csv("C:/Users/Admin/Downloads/Expt 6- Dataset_wisconsinn breast cancerdata_csv.csv")
head(df)
```
scale the data
```{r}
scaled_df<-as.data.frame(scale(df[,3:32]))
head(scaled_df)
```
include the diagnosis columns in scaled_df
```{r}
scaled_df$diagnosis<-df$diagnosis
head(scaled_df)
```
split the data into training and testing sets
```{r}
library(caTools)
set.seed(100)
split_vector<-sample.split(scaled_df$diagnosis,SplitRatio=0.75)
split_vector
train_df<-subset(scaled_df,split_vector==T)
test_df<-subset(scaled_df,split_vector==F)
```

Apply KNN  algorithm 
```{r}
library(class)
knn_model<-knn(train_df[,-31],test_df[,-31],cl=train_df$diagnosis,k=3)
knn_model
```
Save the prediction in the predictions column in test set
```{r}
test_df$predictions<-knn_model
head(test_df)
```
Create a confusion matrix
```{r}
confusion_matrix<-table(Actual=test_df$diagnosis,Predictions=test_df$predictions)
confusion_matrix
```
Let  the positive class be "Maligent" and negative class be "Benign"
Evaluate accuracy
```{r}
accuracy<-sum(diag(confusion_matrix))/sum(confusion_matrix)
cat("Accuray of KNN model is",accuracy*100,"%")
```
Evaluate the sensitivity
```{r}
sensitivity<-confusion_matrix[2,2]/sum(confusion_matrix[2,])
cat("sensitivity of KNN model is",sensitivity*100,"%")
```
Evaluate the specificity
```{r}
specificity<-confusion_matrix[1,1]/sum(confusion_matrix[1,])
cat("specificity of KNN model is",specificity*100,"%")
```
Evaluate the precision
```{r}
precision<-confusion_matrix[2,2]/sum(confusion_matrix[,2])
cat("precision of KNN model is",precision*100,"%")
```


